Get Data

### 2022-02-18 get_data.Rmd
yay figured it out

```{r}
library(dplyr)
library(purrr)
library(bib2df)
library(tidyverse)

@@

@@

@@

```{r}
# thanks SO for this id for the bad coding on scholar 
p_get_scholar_id <- possibly(get_scholar_id, otherwise = NA_character_)
scholars <- character(nrow(get_id))
for(i in 1:10) {
  scholars[i] <- p_get_scholar_id(last_name = get_id$last[i], 
                         first_name = get_id$first[i])

@@

>>>>

```{r}
library(dplyr)
library(purrr)
library(bib2df)
library(tidyverse)
library(httr)

@@

  cat(i)
  cat("\n")

@@

    id <- unique(na.omit(temp_DF$works$`source.assertion-origin-orcid.path`))

@@

- First, fix the scholar package issue that it doesn't correctly pull ids that have punctuation in them.
-

```{r}
get_scholar <- function (last_name = "", first_name = "", affiliation = NA) 
{
    if (!any(nzchar(c(first_name, last_name)))) 
        stop("At least one of first and last name must be specified!")
    site <- getOption("scholar_site")
    url <- paste0(site, "/citations?view_op=search_authors&mauthors=", 
        first_name, "+", last_name, "&hl=en&oi=ao")
    page <- get_scholar_resp(url)
    if (is.null(page)) 
        return(NA)
    aa <- content(page, as = "text")
    ids <- stringr::str_extract_all(string = aa, pattern = ';user=.{12}')

    if (length(unlist(ids)) == 0) {
        message("No Scholar ID found.")
        return(NA)
    }
    ids <- ids %>% unlist %>% gsub(";user=", "", 
        .) %>% unique

    return(ids)
  }
```

- Then determine if you can find scholars matching that information.

```{r}
# thanks SO for this id for the bad coding on scholar 
p_get_scholar_id <- possibly(get_scholar, otherwise = NA_character_)
scholars <- character(nrow(get_id))
for(i in 1:10) {
  id <- NA
  possibles <- p_get_scholar_id(last_name = get_id$last[i], 
                                first_name = get_id$first[i])

  for (q in 1:length(possibles)){

    articles <- get_publications(possibles[q])
    articles$title <- gsub("[[:punct:]]", "", articles$title) 
    articles$title <- tolower(articles$title) 
    temp_DF <- articles %>% 
      filter(title == get_id$TITLE[i])

    if (nrow(temp_DF) > 0){

      if (!is.na(id)){ 
        id <- c(id, possibles[q]) 
        } else { id <- possibles[q] }
    }

  }
  cat(i)
  cat("\n")

  if (length(id) == 1) { scholars[i] <- id }
  if (length(id) > 1) { scholars[i] <- list(id) }

@@

...average citation rates/h index/i10 index
